Testing and Isolation Efficacy: Insights from a Simple Epidemic Model

### 2021-05-03 SIR_manuscript.tex
minor changes

\newcommand{\fref}[1]{Fig.~\ref{#1}}
\newcommand{\Rlogo}{R\xspace}
\newcommand{\percap}{\emph{per capita}\xspace}
\newcommand{\Rnum}{\ensuremath{\mathcal{R}_0}}
\newcommand{\covid}{COVID-19\xspace}
\newcommand{\pro}[1][]{\ensuremath{\frac{\partial #1}{\partial \rho}}}

@@

\jd{$w_R$ does not affect \Rnum, and should not be one of the parameters in the figure title. Prepend with English (random testing and weighting testing).}

@@

We also see that greater test intensity $\rho$ increases the effectiveness of control $\Delta$ ($\Delta$ increases as we move up in each plot in this Figure. Mathematically speaking, we did find a counter-vailing effect, but this can only be seen when we allow $\rho$ to take unrealistically large values, and only for weighted testing (see \fref{pan2}). The explanation here is that more rapid testing leaves more susceptibles in the ``waiting-for-no'' category at the DFE; these people must then wait for their tests to be returned before they can be tested again, receive a positive test, and become cautious. This effect is usually weak compared to the helpful effects of testing, but if testing is weighted, $\theta_w$ is low, and test returns are slow, t is possible for increasing $\rho$ to reduce $\Delta$ (see upper-right part of upper-right plot of \fref{pan2}b).

\ali{Thinking of last column of 2 Figs, moving from top tp bottom as $\theta\_c=1$ and $\theta\_w$ changes from 0 to 1} When $\theta\_c$ is closer to 1 and $\theta\_w$ is closer to 0, increasing $\rho$ combined with deccreasing $1/\omega$ is effective in reducing $\Rnum$. However, as $\theta_w$ is getting closer to 1, increasing $\rho$ combined with increasing $1/\omega$ is better.

% When $\rho$ is closer to 0 (Fig.\,\ref{pan}),  and $\theta_c$ is closer to 0, increasing $\rho$ and decreasing $1/\omega$ is a    
% 
% when $\rho$ is small relative to $N_0$, increasing $\rho$ combined with changes in the test return time $1/\omega$ is always good in general.  
% 
% When the isolation efficay is low, i.e., $\theta\_w$ is closer to 0, speeding up the test reporting processing time can increase $\Rnum$ regardless of the speed of testing. However there is threshold for $1/\omega$ above which prolonging the test return time

% awaiting people (including people in $I\_p$ and $I\_n$ compartments) follow the isolation perfectly, i.e., $\theta\_w$ is closer to 1. However, speeding the test reporting reduces the epidemic more when the awaiting people less follow the isolation, i.e., $\theta\_w$ is closer to 0. 
% 
% Furthermore, we derived an inequality that quantifies the exact relationships between model parameters that result in returning tests more rapidly being favorable \eqref{eq:necsuf}.
% \david{What do we learn from this inequality?  Why is it relegated to an appendix?}

>>>>

\newcommand{\fref}[1]{Fig.~\ref{#1}}
\newcommand{\Rlogo}{R\xspace}
\newcommand{\percap}{\emph{per capita}\xspace}
\newcommand{\Rnum}{\ensuremath{\mathcal{R}_0}}
\newcommand{\covid}{COVID-19\xspace}
\newcommand{\pro}[1][]{\ensuremath{\frac{\partial #1}{\partial \rho}}}
\newcommand\pder[2][]{\ensuremath{\frac{\partial#1}{\partial#2}}} %\pder[x]{y}

@@

@@

We also see that greater test intensity $\rho$ increases the effectiveness of control $\Delta$ ($\Delta$ increases as we move up in each plot in this Figure. Mathematically speaking, we did find a counter-vailing effect, but this can only be seen when we allow $\rho$ to take unrealistically large values, and only for weighted testing (see \fref{pan2}). The explanation here is that more rapid testing leaves more susceptibles in the ``waiting-for-no'' category at the DFE; these people must then wait for their tests to be returned before they can be tested again, receive a positive test, and become cautious. This effect is usually weak compared to the helpful effects of testing, but if testing is weighted, $\theta_w$ is low, and test returns are slow, t is possible for increasing $\rho$ to reduce $\Delta$ (see upper-right part of upper-right plot of \fref{pan2}(b)).
